An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-05-20 Revision/R1_latex/manuscript.tex
flat-file revision version
revision continued

In fact, it is still a very challenging task to efficiently handle
curvature in the context of image segmentation.  State-of-art methods
are in practice difficult to optimize and do not scale easily
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
often unknown. \revision{In the segmentation method of \cite{schoenemann09linear}, for example, the curvature is estimated by a simple formula involving angles and edge lengths at polygon vertices. The quality of the estimation is higly influenced by the number of vertices and where they are located along the curve. More important, in this estimator, the curve representation lies in the continuous domain and the properties of such estimator are not immediately valid when the curve is translated to the digital domain.  In particular, it is not straightforward to include a image data term in this model without adding extra assumptions about the curve representation. One could use a spline approximation with exact curvature information and the same kind of approach would have the same pros and cons.} Improving the quality of the curvature estimator has an important impact on the accuracy of the results, \revision{but we should use the appropriate tools to evaluate its quality. In the context of measurements in digital data, this tool is multigrid convergence.}

@@

\begin{figure}[h!]
	\center
	\subfloat[\label{}]{%
	\includegraphics[scale=2.0]{images/local_search/definitions/flower.png}
	}\hspace{40pt}%
	\subfloat[\label{}]{%	
	\includegraphics[scale=0.3]{images/local_search/definitions/cellular-grid-illustration.eps}
	}
	\caption{\revision{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region. In figure (b), pixels are colored in gray, linels in green and pointels in blue.}}
	\label{fig:cellular-grid-model}
\end{figure}

@@

\begin{figure}[!h]
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.03]{images/local_search/definitions/R3.pdf}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.22]{images/local_search/definitions/glued-curve.eps}
	}%	
	\caption{\revision{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}}
\end{figure}

>>>>

In fact, it is still a very challenging task to efficiently handle
curvature in the context of image segmentation.  State-of-art methods
are in practice difficult to optimize and do not scale easily
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
often unknown. \revision{In the segmentation method of \cite{schoenemann09linear}, for example, the curvature is estimated by a simple formula involving angles and edge lengths at polygon vertices. The quality of the estimation is higly influenced by the number of vertices and where they are located along the curve. More important, in this estimator, the curve representation lies in the continuous domain and the properties of such estimator are not immediately valid when the curve is translated to the digital domain.  In particular, it is not straightforward to include an image data term in this model without adding extra assumptions about the curve representation. One could use a spline approximation with exact curvature information and the same kind of approach would have the same pros and cons.} Improving the quality of the curvature estimator has an important impact on the accuracy of the results, \revision{but we should use the appropriate tools to evaluate its quality. In the context of measurements in digital data, this tool is multigrid convergence.}

@@

\begin{figure}[h!]
	\center
	\subfloat[\label{}]{%
	\includegraphics[scale=2.0]{flower.png}
	}\hspace{40pt}%
	\subfloat[\label{}]{%	
	\includegraphics[scale=0.3]{cellular-grid-illustration.eps}
	}
	\caption{\revision{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region. In figure (b), pixels are colored in gray, linels in green and pointels in blue.}}
	\label{fig:cellular-grid-model}
\end{figure}

@@

\begin{figure}[!h]
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.03]{R3.pdf}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.22]{glued-curve.eps}
	}%	
	\caption{\revision{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}}
\end{figure}
